%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{xcolor}
\usepackage{titlesec}




%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}

 \usepackage{charter}
 


% \pagestyle{fancy}
% \fancyhf{} % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\centering\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item[$\bullet$]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\jobSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1,} #3 & #2 \\
    \ifx&#4&\else\small#4\fi
  \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    %\color{blue}
    \textbf{\huge \scshape Alyssa Sawyer} \\ \vspace{3pt}
    \faEnvelope{} \href{asawyer@hmc.edu}{asawyer@hmc.edu} $\quad$ 
    \faPhone{} \href{tel:6503957429}{(650) 395-7429} $\quad$
    \faLinkedin{} \href{https://www.linkedin.com/in/alysawyer/}{@alysawyer} $\quad$
    \faGlobe{} \href{https://alysawyer.com}{alysawyer.com} $\quad$
    \faGithub{} \href{https://github.com/alysawyer}{@alysawyer} $\quad$
\end{center}




%-----------EXPERIENCE----------- 
\section{Professional Experience}
  \resumeSubHeadingListStart

    
  \jobSubheading
  {Incoming Solutions Architect Intern}{May 2025 - August 2025}
  {NVIDIA}{}
  \begin{itemize}\small
  \setlength\itemsep{0em}
    \resumeItem{NVIDIA Infrastructure Specialists Team (NVIS)}
  \end{itemize}

  
    \jobSubheading
    {Solutions Architect Intern}{May 2024 - August 2024}
    {NVIDIA}{}
    \begin{itemize}\small
    \setlength\itemsep{0em}
      \resumeItem{Lead development of generative AI application with retrieval augmented generation (RAG) using LangChain to rank resumes.}
      \resumeItem{RAG app resulted in immediate impact by accelerating the time to recruit and speed of identification of strong candidates.}
      \resumeItem{Worked with Tier 1 Cloud Service Providers on data center scale validation projects. Supported by traveling onsite.}
      \resumeItem{Owned Edge AI applications by using NVIDIA Jetson products to run deep learning models locally.}
      \resumeItem{Completed Building RAG Agents with LLMs, Fundamentals of Deep Learning, and Deep Learning Institute Instructor courses. }
    \end{itemize}

    \jobSubheading
      {Data Analyst}{January 2023 - June 2024}
      {Claremont Graduate University}{}
      \begin{itemize}\small
      \setlength\itemsep{0em}
        \resumeItem{ Programmed an interactive data visualization website for the CGU Cultural Property Disputes Resource using D3.js.}
        \resumeItem{ Provided a resource for lawyers, journalists, and scholars to track information regarding 400+ cases of stolen artifacts.}
        \resumeItem{ Developed a pipeline to scrape xml of cases into summary statistics used by all data analysts on this project. }
      \end{itemize}
  
    \jobSubheading
      {Software Engineer Intern}{January 2023 - May 2023}
      {Samba TV}{}
      \begin{itemize}\small
      \setlength\itemsep{0em}
        \resumeItem{Architected a synthetic data set by naturally integrating ads in scenes to create 500k+ images using the COCO API.}
        \resumeItem{ Designed logo placement algorithm using Blender Python API. The images are intended to be an open source database.}

      \end{itemize}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Harvey Mudd College}{August 2022 - May 2026}
      {B.S. in \textbf{Computer Science and Math,} Harvey S. Mudd Scholar, Dean's List}{}
        % \begin{itemize}\small
        % \setlength\itemsep{0em}
        % Discrete Mathematics (c), Data Structures/Program Development(c), 
            % \resumeItem{ \textbf{Relevant Coursework:} Data Structures/Program Development, Mathematical Analysis, Discrete Mathematics, Computability and Logic, Probability and Statistics, User Experience Research and Evaluation (TA), Principles of Computer Science.}
            % \resumeItem{ \textbf{Activities:} Inclusive Campus Mentor, P-ai Project Director, Society of Women Engineers. Prev Wellness Director.}
          % \end{itemize}
    \resumeSubheading
      {College of San Mateo, Cañada College, Skyline College, and Foothill College}{August 2019 - June 2022}
      {Concurrent Enrollment Program}{}
        % \begin{itemize}\small
        % \setlength\itemsep{0em}
        %     \resumeItem{ \textbf{Relevant Coursework:} Java Programming Methods, Python Programming, JavaScript for Programmers, Intro to Object-Oriented Program Design, Introduction to Web Design, Ethical Hacking, Linear Algebra, Differential Equations, Calculus III.}
        % \end{itemize}    
    \resumeSubheading
      {Sequoia High School}{August 2018 - June 2022}
      {International Baccalaureate Diploma, CA Scholarship Federation Life Member, Honor Roll}{} 

        
        
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills and Interests}
\begin{itemize}[leftmargin=0.15in, label={}]
   \small{\item{
   \textbf{Relevant Coursework:}{ Data Structures, Algorithms, Computer Vision, Mathematical Analysis, Discrete Mathematics, Computability and Logic, Probability and Statistics, User Experience Research (TA), Principles of Computer Science, Java, Python, JavaScript, Object-Oriented Program Design, Web Design, Ethical Hacking, Abstract Algebra, Advanced Linear Algebra, Differential Equations, Multivariable Calculus.} \\
    \textbf{Skills:}{ Python, Java, C\texttt{++}, JavaScript, R, LaTeX, Linux, Git, Natural Language Processing, Generative AI, Computer Vision.} \\
    \textbf{Libraries:}{ NumPy, Matplotlib, PyTorch, Pandas, Beautiful Soup, OpenCV, Selenium, Gradio, LangChain, Streamlit.} \\
    % \textbf{Leadership:}{Currently debate coaching and Director of Projects at Project AI club, previously President of debate, mock trial, non profit director}
    \textbf{Interests:}{ Building mechanical keyboards, running, photography, debate coaching.} \\
   }}
\end{itemize}

  \section{Research Experience}
    \resumeSubHeadingListStart

    \jobSubheading
    {Founder and President}{September 2024 - Present}
    {Code the Change Harvey Mudd College}{}
    \begin{itemize}\small
    \setlength\itemsep{0em}
      \resumeItem{ Created a technical tech for good club. Lead development of projects with MIT, The Boston Museum of Science, UNHCR, etc. }
      \resumeItem{ Grew club to 25 regular members, 4 projects. Lead leadership team of 5 in creating events and programming.}
      % \resumeItem{Used black box optimization with fmin in Javascript and Pokemon API to reverse engineer information in a battle.}
    \end{itemize}

      % \jobSubheading
      % {Machine Learning Researcher}{August 2024 - January 2025}
      % {Harvey Mudd College}{}
      % \begin{itemize}\small
      % \setlength\itemsep{0em}
      %     % \resumeItem{ Compiled and investigated action attention papers, began development into pipe}
      %     \resumeItem{Led development of a model that predicts drone operator errors in identifying infrastructure faults with over 80\% accuracy.}
      % \end{itemize}

      % \jobSubheading
      % {Director of Projects}{September 2022 - Present}
      % {P-ai Claremont Colleges Club}{}
      % \begin{itemize}\small
      % \setlength\itemsep{0em}
      %   % \resumeItem{ Supporting and leading 5 project managers and guiding them through the process of creating and deploying an application. }
      %   \resumeItem{ Managed a team of 4, fully designed a computer vision project with transfer learning using ResNet with PyTorch.}
      %   % \resumeItem{Used black box optimization with fmin in Javascript and Pokemon API to reverse engineer information in a battle.}
      % \end{itemize}

      \jobSubheading
        {Artificial Intelligence Researcher}{January 2024 - June 2024}
        {Harvey Mudd College}{}
        \begin{itemize}\small
        \setlength\itemsep{0em}
            \resumeItem{ Led development of a model that predicts drone operator errors in identifying infrastructure faults with over 80\% accuracy.}
        \end{itemize}

        \jobSubheading
        {Machine Learning Researcher}{May 2023 - January 2024}
        {Claremont McKenna College}{}
        \begin{itemize}\small
        \setlength\itemsep{0em}
            \resumeItem{ First author of paper at the 29th ACM SIGKDD Conference on Knowledge Discovery and Data Mining’s Data Science Day.}
            \resumeItem{ Finetuned large language models on high quality textbook data to improve performance by 25\% on low resource languages. }
            \resumeItem{ Lead a decrease of OpenAI API usage cost by 70x in the pipeline to compare model performances through analyzing perplexity. }
            \resumeItem{Constructed question answer pairs for finetuning process from a Latin textbook utilizing regular expressions.}
        \end{itemize}

        \jobSubheading
        {Computer Science Researcher}{September 2022 - May 2023}
        {Harvey Mudd College}{}
        \begin{itemize}\small
        \setlength\itemsep{0em}
          \resumeItem{ Created a wearable device for a sensory augmentation experiment using Arduino. Led software and hardware development.}
          \resumeItem{ Integrated the project into a Pitzer College philosophy class to improve student learning with an interactive element.}
        \end{itemize}

        
    \resumeSubHeadingListEnd



%-----------Awards-----------
\section{Awards}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Harvey S. Mudd Scholar} $|$ Received merit award  due to being identified as in the top 2\% of the applicant pool.}{}
    \resumeProjectHeading
          {\textbf{Top 4 Debater in the Country} $|$ Placed in the top 4 at Nationals for Lincoln-Douglas debate, after qualifying out of 20,000+.}{}
    % \resumeProjectHeading{\textbf{Top Student} $|$ Dean's List at Harvey Mudd College, Honor Roll at Sequoia High School}{}
    % \resumeProjectHeading
          \resumeProjectHeading{\textbf{300+ Volunteer Hours} $|$ At 30+ organizations through the National Charity League. Received Presidential Bronze Volunteer Award.}{}
    %       \resumeProjectHeading
          \resumeProjectHeading{\textbf{Nonprofit Founder} $|$ Founded and ran a debate camp nonprofit for 200+ underprivileged debaters during COVID-19 for three years.}{}

    \resumeSubHeadingListEnd
  

%

%-------------------------------------------
\end{document}
