%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{xcolor}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}

 \usepackage{charter}
 


% \pagestyle{fancy}
% \fancyhf{} % clear all header and footer fields
% \fancyfoot{}r
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    %\color{blue}
    \textbf{\huge \scshape Alyssa Sawyer} \\ \vspace{3pt}
    \faEnvelope{} \href{asawyer@hmc.edu}{asawyer@hmc.edu} $\quad$ 
    \faPhone{} \href{tel:6503957429}{(650) 395-7429} $\quad$
    \faLinkedin{} \href{https://www.linkedin.com/in/alysawyer/}{@alysawyer} $\quad$
    \faGlobe{} \href{https://alysawyer.com}{alysawyer.com} $\quad$
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Harvey Mudd College}{August 2022 - May 2026}
      {Bachelor of Science in \textbf{Computer Science and Math}, Dean's List}{}
        \begin{itemize}\small
        \setlength\itemsep{0em}
        % Discrete Mathematics (c), Data Structures/Program Development(c), 
            \item[--] \textbf{Relevant Coursework:} Data Structures/Program Development, Mathematical Analysis, Discrete Mathematics, Computability and Logic, Probability and Statistics, User Experience Research and Evaluation (TA), Principles of Computer Science.
            % \item[--] \textbf{Activities:} Wellness Director, Inclusive Campus Mentor, Mechanical Keyboard Club President, Society of Women Engineers. 
          \end{itemize}
    \vspace{-5pt}
    \resumeSubheading
      {Sequoia High School}{August 2018 - June 2022}
      {International Baccalaureate Diploma, GPA: 4.45/4.0, CA Scholarship Federation Life Member, Honor Roll}{} 
    \vspace{5pt}
    \resumeSubheading
      {College of San Mateo, Cañada College, Skyline College, and Foothill College}{August 2019 - June 2022}
      {Dual Enrollment Program}{}
        \begin{itemize}\small
        \setlength\itemsep{0em}
            \item[--] \textbf{Relevant Coursework:} Java Programming Methods, Python Programming, JavaScript for Programmers, Intro to Object-Oriented Program Design, Introduction to Web Design, Ethical Hacking, Linear Algebra, Differential Equations, Calculus III.
        \end{itemize}    
        
        
  \resumeSubHeadingListEnd


%-----------EXPERIENCE----------- 
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Solutions Architect Intern}{May 2024 - Present}
    {NVIDIA}{}
    \begin{itemize}\small
    \setlength\itemsep{0em}
      \item[--] Developing a RAG pipeline to rank 500+ resumes using LangChain, NVIDIA foundational models and Streamlit. 
      \item[--] Ran tests to validate GPU cluster performance for external clients. Successfully completed team wide presentations. 
    \end{itemize}

    % \resumeSubheading
    % {Data Analyst}{January 2023 - Present}
    % {Claremont Graduate University}{}
    % \begin{itemize}\small
    % \setlength\itemsep{0em}
    %   \item[--] Programming an interactive data visualization website for the CGU Cultural Property Disputes Resource using D3.js.
    %   \item[--] Providing a resource for lawyers, journalists, and scholars to track information regarding 400+ cases of stolen artifacts.
    % \end{itemize}
  
    \resumeSubheading
      {Software Engineer Intern}{January 2023 - May 2023}
      {Samba TV}{}
      \begin{itemize}\small
      \setlength\itemsep{0em}
        \item[--] Developed a synthetic data set by naturally integrating ads in scenes to create 500k+ images using the COCO API.
        \item[--] Generated logo placement using Python in Blender. These pictures are intended to be released as an open source database.

      \end{itemize}
  \resumeSubHeadingListEnd


  \section{Research Experience}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Artificial Intelligence Researcher}{January 2024 - June 2024}
        {Harvey Mudd College, advised by Professor David Nembhard}{}
        \begin{itemize}\small
        \setlength\itemsep{0em}
            \item[--] Creating a model that analyzes biometric EEG data to predict drone operator errors when identifying infrastructure faults.
        \end{itemize}

        \resumeSubheading
        {Machine Learning Researcher}{May 2023 - January 2024}
        {Claremont McKenna College, advised by Professor Mike Izbicki}{}
        \begin{itemize}\small
        \setlength\itemsep{0em}
            \item[--] First author of paper at the 29th ACM SIGKDD Conference on Knowledge Discovery and Data Mining’s Data Science Day.
            \item[--] Finetuning large language models on high quality textbook data to improve performance by 25\% on low resource languages. 
            \item[--] Decreased OpenAI API usage cost by 70x in the pipeline to compare baseline model performance to our modified models. Done through developing a program to calculate the lowest perplexity option of multiple choice quiz questions.
        \end{itemize}

        \resumeSubheading
        {Computer Science Researcher}{September 2022 - May 2023}
        {Harvey Mudd College, advised by Professor Lucas Bang}{}
        \begin{itemize}\small
        \setlength\itemsep{0em}
          \item[--] Created a wearable device for a sensory augmentation experiment using Arduino. Led software and hardware development.
          % \item[--] Integrated the project into a Pitzer College philosophy class to improve student learning with an interactive element.
  
        \end{itemize}
        
    \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Data Analyst}{January 2023 - Present}
      {Claremont Graduate University}{}
      \begin{itemize}\small
      \setlength\itemsep{0em}
        \item[--] Programming an interactive data visualization website using D3.js for 400+ cases of stolen artifacts for journalists and scholars.
        % \item[--] Providing a resource for lawyers, journalists, and scholars to track information regarding 400+ cases of stolen artifacts.

      \end{itemize}
    \resumeSubheading
    {Machine Learning Project Lead}{September 2022 - Present}
    {P-ai Claremont Colleges Club}{}
    \begin{itemize}\small
    \setlength\itemsep{0em}
      \item[--] Managing a team of 4, fully designed a computer vision project with transfer learning using ResNet with PyTorch.
      % \item[--] P-okemon: Used black box optimization with fmin in Javascript and Pokemon API to reverse engineer information in a battle.

    \end{itemize}
  \resumeSubHeadingListEnd
universal-darwin
%-----------TEACHING-----------
\section{Teaching}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Instructor}{January 2023 - Present}
      {Self Employeed}{}
      \begin{itemize}\small
      \setlength\itemsep{0em}
        \item[--] Held private sessions for 10+ students based on their individual needs. Developed unique curriculum tracks based on individual needs.
        \item[--] Coached students from novice level to qualifying to nationals and winning tournaments. 

      \end{itemize}
    \resumeSubheading
  
    {Summer Instructor and Founder}{September 2022 - January 2023}
    {The Debate Intensive (TDI) and Online Debate Institute (ODI)}{}
    \begin{itemize}\small
    \setlength\itemsep{0em}
      \item[--] TDI: Lead a classroom of 20+ students for 3 consecutive summers. Taught argument generation, complexities in current events, and research skills. 
      \item[--] ODI: Founded and developed curriculm for free debate camp, managed all admin tasks and logistics. Helped 200+ underresourced students save 900k+.
    \end{itemize}
    \end{itemize}
  \resumeSubHeadingListEnd

%-----------Awards-----------
\section{Awards}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Harvey S. Mudd Scholar} $|$ \emph{Received merit award  due to being identified as in the top 2\% of the applicant pool.}}{}
    \resumeProjectHeading
          {\textbf{Top 4 Debater in the Country} $|$ \emph{Placed in the top 4 at Nationals for Lincoln-Douglas debate, after qualifying out of 20,000+.}}{}
    % \resumeProjectHeading
    %       {\textbf{300+ Volunteer Hours} $|$ \emph{At 30+ organizations through the National Charity League. Received Presidential Bronze Volunteer Award.}}{}
    %       \resumeProjectHeading
    %       {\textbf{Nonprofit Founder} $|$ \emph{Founded and ran a 2-week debate camp nonprofit for 200+ underprivileged debaters during COVID-19 for three years.}}{}

    \resumeSubHeadingListEnd
  

%
%-----------PROGRAMMING SKILLS-----------
\section{Skills and Interests}
\begin{itemize}[leftmargin=0.15in, label={}]
   \small{\item{
    \textbf{Skills:}{ Python, Java, C++, JavaScript, HTML, CSS, R, LaTeX, JSON, Linux, Git, Natural Language Processing, Excel.} \\
    \textbf{Libraries:}{ NumPy, Matplotlib, PyTorch, Pandas, Beautiful Soup, OpenCV, Selenium, Gradio.} \\
    \textbf{Interests:}{ Building mechanical keyboards, running, photography, debate coaching.} \\
    % \textbf{Frameworks:}{ Hugo, WordPress} \\
    % \textbf{Developer Tools:}{ CHANGE Visual Studio Code, PyCharm, IntelliJ, Eclipse, Xcode, RStudio, Arduino} \\
   }}
\end{itemize}

%-------------------------------------------
\end{document}
